---
date: "2021-10-08"
draft: false
excerpt: But what should we do with a fiction that is not blatantly false, but false only because an author has been forgetful? . . . 
subtitle: ""
title: On Truth and Fiction 
weight: 1
---

"But what should we do with a fiction that is not blatantly false, but false only because an author has been forgetful"? (truth and fiction, 46) In other words, why can't we ascribe the same subject-predicate form as parallel descriptions of real-life characters; such that it would be false to say "Holmes wears a silk top hat" in the same way that it would be false to say "Nixon wears a silk top hat."

As it stands now, several difficulties arise in doing so:

* In some ways, Holmes is a real-life person of flesh and blood as is Nixon.
* How many members are there in Sir Joseph's chorus, *five*? *fifty*?
* What restricts ranges of quantification.
* Finally, why are fictional characters immune to inferred consequences?

> . . . the Meinongian must tell us why truths about fictional characters are cut off, sometimes though not always, from the consequences they ought to imply (37).

The answer to this question, argues Lewis is that we must first abstract away from the original to several of the possible revisions that remain closest to the original.

```{r echo=F, fig.cap="\\label{fig:figs}Closest Worlds"}
DiagrammeR::grViz("digraph {
  graph [layout = dot, rankdir = TB]
  
  node [shape = oval]        
  rec1 [label = <Actual World; &#x3C8;@^{1}w@_{0}>]
  rec2 [label = 'Nearest w@_{1}']
  rec3 [label =  'Nearest w@_{2}']
  rec4 [label = 'Nearest w@_{3}']
  
  # edge definitions with the node IDs
  rec1 -> rec2 -> rec3 -> rec4
  }",
  height = 500)

```

Lets say that at $w_{1}$, "Baker Street" is closer to "Paddington" than it is to "Waterloo." Also at $w_{1}$ Sherlock Holmes has $10^{5}$ number of hairs on his head. While we might think that in the actual world $w_{0}$, it is also true that "Baker Street" is closer to "Paddington" than it is to "Waterloo," but this gives us no reason to think that Sherlock Holmes has $10^{5}$ number of hairs on his head. Therefore there are a number of truths $\psi^{1-n}$ which hold at $w_{1}$.

```{r echo=F, fig.cap="\\label{fig:figs}Relations"}
DiagrammeR::grViz("digraph {
  graph [layout = dot, rankdir = TB]
  
  node [shape = oval]        
  rec1 [label = 'Actual World, w@_{0}']
  rec2 [label = 'Nearest w@_{1} psi@^{1-n}']
  rec3 [label =  'Nearest w@_{2}']
  rec4 [label = 'Nearest w@_{3}']
  
  # edge definitions with the node IDs
  rec1 -> rec2  rec1 -> rec4
  }",
  height = 500)

```

The above is wrong because Sherlock Holmes does not appear to have $10_{5}$ number of hairs on his head. What this unfortunate sequence looks like is:

## The Reality Principle

If $p_{1}, . . . p_{n}$ are the propositions whose fictionality a representation generates directly, another proposition, $q$, is fictional in it if, and only if, were it the case that $p_{1}, . . . p_{n}$, it would be the case that $q$.

$$\frac{\psi^{1}, . . ., \psi^{n}}{\therefore\phi}$$

Where there is a $w_{n}$ between $w_{1-n}$ at which $\neg\psi\land\phi$. You might think that there is no reason to think that Sherlock Holmes has $10^{5}$ number of hairs on his head anywhere in the set $\psi_{1-n}$ but if this is true, then it does not answer those cases where:

* Holmes lived on Baker Street (which is not nearer Paddington Station than it is Waterloo Station in the actual world $w_{0}$)
* Holmes lived nearer to Paddington Station than Waterloo Station
* Holmes was just a person---a person of flesh and blood (Not person of flesh and blood at $w_{0}$)
* Holmes really existed (doesn't exist?)

The interpreter of the fiction is to ask: "what the real world would be like if the propositions (as a whole within fiction) whose fictionality is generated directly were true: What else would be true if they were?"

We can possibly amend this problem by prefixing an operator; say "In the fiction $f$ . . .", to each premiss and to the conclusion of the original arguments.

$$\frac{In f, \psi^{1}, . . ., In f, \psi^{n}}{\therefore In f, \phi}$$
